Graphics

### 2020-06-02 individual-cohorts/graphics_t_statistics.Rmd
remove missing values for certain comparisons

df <- inner_join(mpp_acc, mpp_dlpfc,
                 by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_dsACC, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_stg, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_sgACC, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_dlpfc, by = c("Comparison", "gene_id"))
#Remove transcript Ids
df <- df %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df <- inner_join(df, CMC1, by = c("Comparison", "gene_id")) 
df <- inner_join(df, CMC_HBCC, by = c("Comparison", "gene_id"))
df <- inner_join(df, gandal, by = c("Comparison", "gene_id"))

@@

# Control vs Other
```{r plota, fig.width = 20, fig.height = 40}
df_one <- df[df$Comparison %in% "Control_vs_Other",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

@@

# Control vs SCZ
```{r plotb, fig.width = 20, fig.height = 40}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

plot_t(df_two, conditions)
```

@@

# Other vs SCZ
```{r plotc, fig.width = 20, fig.height = 40}
df_three <- df[df$Comparison %in% "Other_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id")

plot_t(df_three, conditions)
```

>>>>

df <- inner_join(mpp_acc, mpp_dlpfc,
                 by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_dsACC, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_stg, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_sgACC, by = c("Comparison", "gene_id"))
df <- inner_join(df, hbcc_dlpfc, by = c("Comparison", "gene_id"))
#Remove transcript Ids
df <- df %>% 
  separate(gene_id, c("gene_id", "transcript")) %>% 
  dplyr::select(-one_of("transcript"))
df <- left_join(df, CMC1, by = c("Comparison", "gene_id")) 
df <- left_join(df, CMC_HBCC, by = c("Comparison", "gene_id"))
df <- left_join(df, gandal, by = c("Comparison", "gene_id"))

@@

# Control vs Other
```{r plota, fig.width = 20, fig.height = 40}
df_one <- df[df$Comparison %in% "Control_vs_Other",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

@@

# Control vs SCZ
```{r plotb, fig.width = 20, fig.height = 40}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

conditions <- gtools::combinations(n = ncol(df_two), 2, seq_len(ncol(df_two)))
plot_t(df_two, conditions)
```

@@

# Other vs SCZ
```{r plotc, fig.width = 20, fig.height = 40}
df_three <- df[df$Comparison %in% "Other_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

conditions <- gtools::combinations(n = ncol(df_three), 2, seq_len(ncol(df_three)))
plot_t(df_three, conditions)
```
